### 2016-02-15 paper/4-performance.tex
Made plots a tiny bit bigger (0.88 --> 0.9)
Fix typo.

\newcommand{\plotfraction}{0.88}

@@

\subsubsection{Queue}
In the Queue model, we increase both width and depth simultaneously.
For example, the $400$ models configuration is obtained with a width and depth of $20$.
As can be seen in Figure~\ref{fig:Queue_benchmark}, dxex considerably outperforms adevs.
Through profiling, we found that adevs spends much time routing the simulation messages (\textit{e.g.}, \textit{*}, \textit{@}) through the hierarchy, whereas dxex avoids this throuhg its flattened model structure.
Both simulation tools have similar complexities, though dxex is much faster thanks to its more efficient simulation control algorithms.

@@

\subsubsection{Remarks}
Both dxex and adevs use \texttt{tcmalloc} as memory allocator, allowing for thread-local allocation.
Additionally, dxex uses memory pools to further reduce the frequency of expensive system calls (\textit{e.g.}, malloc and free).
\texttt{tcmalloc} only gradually releases memory back to the OS, whereas our pools will not do so at all.
Due to our motivation for memory usage analysis, we will only measure peak allocation.
Profiling is done using Valgrind's massif tool~\cite{Nethercote:2007:VFH:1273442.1250746}.
\vspace{1cm}

>>>>

\newcommand{\plotfraction}{0.9}

@@

\subsubsection{Queue}
In the Queue model, we increase both width and depth simultaneously.
For example, the $400$ models configuration is obtained with a width and depth of $20$.
As can be seen in Figure~\ref{fig:Queue_benchmark}, dxex considerably outperforms adevs.
Through profiling, we found that adevs spends much time routing the simulation messages (\textit{e.g.}, \textit{*}, \textit{@}) through the hierarchy, whereas dxex avoids this through its flattened model structure.
Both simulation tools have similar complexities, though dxex is much faster thanks to its more efficient simulation control algorithms.

@@

\subsubsection{Remarks}
Both dxex and adevs use \texttt{tcmalloc} as memory allocator, allowing for thread-local allocation.
Additionally, dxex uses memory pools to further reduce the frequency of expensive system calls (\textit{e.g.}, malloc and free).
\texttt{tcmalloc} only gradually releases memory back to the OS, whereas our pools will not do so at all.
Due to our motivation for memory usage analysis, we will only measure peak allocation.
Profiling is done using Valgrind's massif tool~\cite{Nethercote:2007:VFH:1273442.1250746}.
